Multi-channel Kondo model URG

### 2021-11-16 multi-channel-urg.tex
removed typos and exhausted the list of possible effective Hamiltonians (i missed some prev.)

\documentclass[12pt]{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Derivation of URG equations for the multi-channel Kondo model}

@@

	H_\text{eff}^{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] \\
+ \frac{J^2}{4}\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\chi_{s_\text{tot}}^{-s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}} H_0 + \frac{\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}{\chi_{s_\text{tot}}^{-s_\text{tot}^z}} s^+_\text{tot}X_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]

@@

	H_\text{eff}^{\frac{1}{2}, 0, 0} &= H_0\\
	H_\text{eff}^{\frac{1}{2}, 1, 1} &= H_0 + \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 + \frac{1}{2 E_\text{gs}} s^+_\text{tot}X_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
	H_\text{eff}^{\frac{1}{2}, 1, -1} &= H_0 - \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{1}{E_\text{gs}} H_0 - \frac{1}{2 E_\text{gs}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + \frac{1}{E_\text{gs}^2} H_0^2 - \frac{1}{E_\text{gs}^3} Z_{1,\text{tot}} H_0\right] \\
	H_\text{eff}^{\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{1}{E_\text{gs} + J/2} H_0 + \frac{1}{2 E_\text{gs} + J} \left(s^+_\text{tot}X_{1,\text{tot}} - s^-_\text{tot}X^\dagger_{1,\text{tot}}\right) \right.\\
					 &\left.+ \frac{2}{\left(E_\text{gs} + J/2\right)^2} H_0^2 - \frac{2}{\left(E_\text{gs} + J/2\right)^3} Z_{1,\text{tot}} H_0\right] \\

@@

	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c^\dagger_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c^\dagger_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\

>>>>

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\numberwithin{equation}{section}
\allowdisplaybreaks
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Derivation of URG equations for the multi-channel Kondo model}

@@

	H_\text{eff}^{\frac{1}{2}, s_\text{tot}, s^z_\text{tot}} = H_0 + \frac{J}{2}s^z_\text{tot} + \frac{J^2}{4}\left( \frac{1}{2} + S_d^z \right) \gamma_{s_\text{tot}}^{s_\text{tot}^z}\chi_{s_\text{tot}}^{s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}} H_0 - \frac{\gamma_{s_\text{tot}}^{s_\text{tot}^z}}{\chi_{s_\text{tot}}^{s_\text{tot}^z}} s^-_\text{tot}X^\dagger_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right] \\
+ \frac{J^2}{4}\left( \frac{1}{2} - S_d^z \right)\gamma_{s_\text{tot}}^{-s_\text{tot}^z}\chi_{s_\text{tot}}^{-s_\text{tot}^z}\left[1 + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}} H_0 + \frac{\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}{\chi_{s_\text{tot}}^{-s_\text{tot}^z}} s^+_\text{tot}X_{1,\text{tot}} + {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^2 H_0^2 - {\gamma_{s_\text{tot}}^{-s_\text{tot}^z}}^3 Z_{1,\text{tot}} H_0\right]

@@

	H_\text{eff}^{\pm\frac{1}{2}, 0, 0} &= H_0\\
	H_\text{eff}^{\pm\frac{1}{2}, 1, \pm 1} &= H_0 + \frac{J}{2}\\
	H_\text{eff}^{-\frac{1}{2}, 1, 1} &= H_0 + \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}} + \frac{s^+_\text{tot}X_{1,\text{tot}}}{2 E_\text{gs}} + \frac{H_0^2 }{E_\text{gs}^2} - \frac{Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \\
	H_\text{eff}^{\frac{1}{2}, 1, -1} &= H_0 - \frac{J}{2} + \frac{J^2}{4}\frac{2}{E_\text{gs}}\left[1 + \frac{H_0}{E_\text{gs}}  - \frac{s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 E_\text{gs}}  + \frac{H_0^2}{E_\text{gs}^2}  - \frac{ Z_{1,\text{tot}} H_0}{E_\text{gs}^3}\right] \\
	H_\text{eff}^{-\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{ H_0}{E_\text{gs} + J/2} + \frac{ s^+_\text{tot}X_{1,\text{tot}}}{2 E_\text{gs} + J} + \frac{H_0^2}{\left(E_\text{gs} + J/2\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + J/2\right)^3} \right] \\
	H_\text{eff}^{\frac{1}{2}, 1, 0} &= H_0 + \frac{J^2}{4}\frac{2}{E_\text{gs} + J/2}\left[1 + \frac{ H_0}{E_\text{gs} + J/2} - \frac{ s^-_\text{tot}X^\dagger_{1,\text{tot}}}{2 E_\text{gs} + J} + \frac{H_0^2}{\left(E_\text{gs} + J/2\right)^2} - \frac{Z_{1,\text{tot}} H_0}{\left(E_\text{gs} + J/2\right)^3} \right] \\

@@

	s^+_\text{tot}X_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \downarrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{k_2, \downarrow, l_2}c_{q_2, \uparrow, l_2}\\
	s^-_\text{tot}X^\dagger_{1,\text{tot}} &= \sum_{k_1,q_1,k_2,q_2,l_1,l_2}c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \uparrow, l_1} \left(\epsilon_{k_2}^{l_2} - \epsilon_{q_2}^{l_2}\right) c^\dagger_{q_2, \uparrow, l_2}c_{k_2, \downarrow, l_2}\\
	Z_{1,\text{tot}} H_0 &= \sum_{k_1,q_1,k_2,\sigma_2,l_1,l_2}\left(\epsilon_{k_1}^{l_1} - \epsilon_{q_1}^{l_1}\right) \epsilon_{k_2}^{l_2} \left(c^\dagger_{k_1, \uparrow, l_1}c_{q_1, \uparrow, l_1} - c^\dagger_{k_1, \downarrow, l_1}c_{q_1, \downarrow, l_1}\right) \hat n_{k_2,\sigma_2,l_2}\\
